---
title: "ABM"
author: "Astrid Elmann Hansen"
date: '2022-06-11'
output: html_document
---


> Issues:

No penalty for not cooperating
Agents have no reason to prioritize more than one person
When sorting for higest sat - what if two are similar? How do we sort?
> Simple: random choice




> intercept, 4 forskellige "grundtyper" arbejd samme imod etc eller random evt. kod begge dele
> evt. cost penalty på ikke at arbejde sammen

TODO
Add intercept + cost penalty
Viz sat + dep
Add choice from type (own.etc)
Add commit


# Pure interdependence theory

All agents are connected

Friendships don't deteriorate

Agents can't be alone

ka, kp and kj are constant and identical for all agents

cl_sat and cl_alt traits are constant pr. agent and independent of dyads

dep = dep + ((outcome – cl_alt) / ticks_spent_tog)

sat = sat + ((outcome – cl_sat) / ticks_spent_tog)
    
ka = 2
kp = 2
kj = 0

if dep = positive
  ac = ka/dep
  pc = dep/kp
  
if dep = negative
  ac = dep/ka
  pc = kp/dep



```{r}
pacman::p_load(tidyverse)
source("functions/dates.R")
source("functions/invitations.R")
source("functions/generate_matrix.R")
source("functions/matrix_choice.R")
source("functions/update_dyads.R")
empty_matrix <- read_csv("functions/empty_matrix.csv")
```

```{r setup values}
ka <- 2
kp <- 2

N <- 10 # number of agents

sort <- "sat" # sort by sat or commit?

invite_function <-"prob.invite" # prob.invite or simple.invite?

ticks <- 10 # how many ticks to run

```

```{r setup dyads}
sat <- sample(-10:10, N^2, replace = TRUE) # integers 
dep <- sample(-10:10, N^2, replace = TRUE) # integers 

# sat <- runif(N^2, min = -1) # norm 
# dep <- runif(N^2, min = -1) # norm 

#sat = as.numeric(rep(initial_sat,N^2)) # simple value
#dep = as.numeric(rep(initial_dep,N^2)) # simple value

dep[dep==0] <- 0.001 # lololol

dyads <- tibble(agent_1 = as.numeric(rep(1:N, each=N)), # create df with dyads and inital values
                agent_2 = as.numeric(rep(seq(1:N),N)),
                sat = sat,
                dep = dep,
                ticks_tog = 0,
                outcome = 0)
  
dyads <- dyads %>% filter(agent_1 != agent_2) # Remove dyads with the same agent twice

dyads_his <- dyads %>% mutate(tick = 0) # history dyads
```

```{r setup traits}
traits <- tibble(agent = as.numeric(seq(1:N)),
                 cl_alt = sample(-10:10, N, replace = TRUE),
                 cl_sat = sample(-10:10, N, replace = TRUE))
```

```{r}
start <- proc.time() # start a stopwatch

for (tick in 1:ticks){

hangout <- dates(N = N, dyads = dyads, sort = sort, invite_function = invite_function) # set up date pairs

for (i in 1:nrow(hangout)){ # for every dyad
  
  A <- hangout$A[i] # get the "name" of each agent
  B <- hangout$B[i]
  
  matrix <- generate.matrix(A = A, B = B, matrix = empty_matrix, 
                            dyads = dyads, ka = ka, kp = kp) # generate matrix
  
  A_choice <- own.max(agent = "A", matrix = matrix) # each agent chooses
  B_choice <- own.max(agent = "B", matrix = matrix)

  dyads <- update.dyads(A = A, B = B, A_choice = A_choice, B_choice = B_choice, 
                        matrix = matrix, dyads = dyads) # update dyads
}

dyads_tick <- dyads %>% mutate(tick = tick) # for history dyads
dyads_his <- bind_rows(dyads_his, dyads_tick) # add this tick dyad to dyad_his
dyads <- dyads %>% mutate(outcome = 0) # reset outcomes
  
print(sprintf("Tick %s of %s", tick, ticks))

}
write_csv(dyads_his, "dyads_his.csv")
proc.time() - start # get stopwatch time
```




