---
title: "ABM"
author: "Astrid Elmann Hansen"
date: '2022-06-11'
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

**Format**

All agents are connected

Friendships don't deteriorate

Agents can't be alone

No joint action in matrix

ka and kp are constant and identical for all agents

cl_sat and cl_alt traits are constant pr. agent and independent of dyads


TODO 

Add choice from type (own.etc)
More types of random intercepts?
Commit? or Com?


**Decisions not documented in original design**

Agents choose whom to invite based on probability. Low sat = low prob
of choosing to invite the agent. See code below from invitations.R

```{r eval=FALSE}
 # add the abs value of the min sat to all sat - lowest sat value is now 0
 abs_sort = sat + abs(min(sat))
 # add a row with probability of choosing each agent - finding %
 prob = abs_sort/sum(abs_sort) 
 # 1 random number between 1 and the number of rows in choice
 n <- sample(x = 1:nrow(choice), size = 1, prob = prob) 
```


```{r}
pacman::p_load(tidyverse)
source("functions/dates.R")
source("functions/invitations.R")
source("functions/generate_matrix.R")
source("functions/matrix_choice.R")
source("functions/update_dyads.R")
empty_matrix <- read_csv("functions/empty_matrix.csv", show_col_types = FALSE)
```

>if dep = positive 
>ac = ka/dep 
>pc = dep/kp

>if dep = negative 
>ac = dep/ka 
>pc = kp/dep

```{r setup values}
ka <- 2
kp <- 2

N <- 10 # number of agents MUST BE EVEN NUMBER

ticks <- 100 # how many ticks to run

sort <- "sat" # sort by sat or commit?

invite_function <- "probinvite" # prob or simple?

intercept <- "random" # random or none?

```

```{r setup dyads}
sat <- sample(-10:10, N^2, replace = TRUE) # integers 
dep <- sample(-10:10, N^2, replace = TRUE) # integers 

# sat <- runif(N^2, min = -1) # uniform dist -1 to 1
# dep <- runif(N^2, min = -1) # uniform dist -1 to 1

# sat = as.numeric(rep(0.1,N^2)) # simple value
# dep = as.numeric(rep(0.1,N^2)) # simple value

```

```{r setup traits}
cl_alt <-  sample(-10:10, N, replace = TRUE)
cl_sat <-  sample(-10:10, N, replace = TRUE)
inv    <-  sample(-10:10, N, replace = TRUE)
```

> No touchy
**No touchy**
> No touchy

```{r setup dyads}
dyads <- tibble(agent_1 = as.numeric(rep(1:N, each=N)), # create df with dyads and inital values
                agent_2 = as.numeric(rep(seq(1:N),N)),
                sat = sat,
                dep = dep,
                commit = 0,
                tick_no = 0,
                ticks_tog = 0,
                outcome = 0,
                out_sat = 0,
                out_dep = 0
                )
  
dyads <- dyads %>% filter(agent_1 != agent_2) # Remove dyads with the same agent twice

dyads_his <- dyads
```

```{r setup traits}
traits <- tibble(agent  = as.numeric(seq(1:N)),
                 cl_alt = cl_alt,
                 cl_sat = cl_sat,
                 inv    = inv)
```

```{r}
start <- proc.time() # start a stopwatch

for (tick in 1:ticks){

  hangout <- dates(N = N, dyads = dyads, sort = sort, invite_function = invite_function) # set up date pairs

for (i in 1:nrow(hangout)){ # for every dyad
  
  A <- hangout$A[i] # get the "name" of each agent
  B <- hangout$B[i]
  
  matrix <- generate.matrix(A = A, B = B, matrix = empty_matrix, 
                            dyads = dyads, ka = ka, kp = kp, intercept = intercept) # generate matrix
  
  A_choice <- own.max(agent = "A", matrix = matrix) # each agent chooses
  B_choice <- own.max(agent = "B", matrix = matrix)

  dyads <- update.dyads(A = A, B = B, A_choice = A_choice, B_choice = B_choice, 
                        matrix = matrix, dyads = dyads) # update dyads with new outcomes, tick_tog, sat and dep
}

dyads <- dyads %>% mutate(tick_no = tick) # for history dyads
dyads_his <- bind_rows(dyads_his, dyads) # add this tick dyad to dyad_his
dyads <- dyads %>% mutate(outcome = 0) # reset outcomes
  
print(sprintf("Tick %s of %s", tick, ticks))

}
filename <- sprintf("logfiles/%s_ticks_%s_agents_%s_%s.csv", ticks, N, sort, invite_function)
dyads_his  %>% write_csv(filename)
proc.time() - start # get stopwatch time
```
