---
title: "Pseudocode"
author: "Astrid Elmann Hansen"
date: '2022-06-08'
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r}
pacman::p_load(tidyverse)
set.seed(35)
```


# Pure interdependence theory

All agents are connected

Friendships don't deteriorate

Agents can't be alone

cl_sat and cl_alt traits are constant pr. agent and independent of dyads

ka and kp are constant and identical for all agents

All agents opt to choose OwnMax in matrices

Joint control = 1

Uden intercept

> When sorting for higest sat - what if two are similar? How do we sort?

```{r notes}
# agent
for each agent
  cl_sat
  cl_alt
  for each dyad
    dep = sum (outcome – cl_alt) / ticks_spent_tog
    sat = sum (outcome – cl_sat) / ticks_spent_tog
    
# global
ka = 2
kp = 2
kj = 0

if dep = positive
  ac = ka/dep
  pc = dep/kp
  
if dep = negative
  ac = dep/ka
  pc = kp/dep

```

```{r tibble setup}
N <- 6 # number of agents
initial_dep <- 0.1 # the dependence value all dyads start with
initial_sat <- 0.1 # the satisfaction value all dyads start with

agents <- seq(1:N)
```


```{r tibble setup}
invit <- tibble(agent = as.numeric(agents), # create empty invit table with all agents 
                date = rep(FALSE,N), 
                to = as.numeric(rep(NA,N)), 
                with = as.numeric(rep(NA,N)))

hangout <- tibble(agents = numeric(), # create empty hangout table
                  date = logical(), 
                  to = numeric(), 
                  with = numeric())

dyads <- tibble(agent_1 = as.numeric(rep(1:N, each=N)), # create df with dyads and inital values
                agent_2 = as.numeric(rep(seq(1:N),N)),
                sat = as.numeric(rep(initial_sat,N^2)),
                dep = as.numeric(rep(initial_dep,N^2)))
  
dyads <- dyads %>% filter(agent_1 != agent_2) # Remove dyads with the same agent twice

```

```{r test}
for (agent in invit$agents){ print(agent) }

rows <- sample(nrow(invit))
random_invit <- invit[rows, ]

for (agent in random_invit$agents){ print(agent) }
```
```{r}
agent <- 1
choice <- dyads %>% # make a df from dyads
        filter(agent_1 == agent) %>% # only choose current agent
        filter(!(agent_2 %in% invit)) %>% # remove agents that already have a date (are no longer in invit)
        arrange(desc(sat)) # sort so agent with higest sat is on top #@
      invit_agent <- choice$agent_2[1] # select top agent
      agent_index <- which(invit$agent == agent) # get the row number for the current agent in invit
      invit$to[agent_index] <- invit_agent # in invit set agent choice (might need where() here ?)
```


```{r}
while (nrow(invit) != 0){ # while some agents are left in invite-phase

############################### Send invites ###################################
    for (agent in invit$agents){ # each agent sends invites
        choice <- dyads %>% # make a df from dyads
        filter(agent_1 == agent) %>% # only choose current agent
        filter(agent_2 %in% invit) %>% # remove agents that already have a date (are no longer in invit)
        arrange(desc(sat)) # sort so agent with higest sat is on top #### OBS! What i secondary sort????? ####
      invit_agent <- choice$agent_2[1] # select top agent
      invit$to[agent] <- invit_agent # in invit set agent choice (might need where() here ?)
    }
####################### Check for mutual invites ###############################
      for each agent in invit # each agent checks whether they have mutual invites
        invit_agent <- invit$to[agent] # the agent i invited
        if invit$to[invit_agent] == agent # if the invite from my invit_agent is to me
          invit$date[agent] <- TRUE # set that i have a date
          invit$with[agent] <- invit_agent # set that it is with the person i invited

############################ Update invit df ###################################          
    hangout_dyads <- invit %>% filter(date == TRUE) # select chosen dyads
    hangout <- rbind(hangout, hangout_dyads) # append dyads to hangout df
    invit <- invit %>% filter(date == FALSE) %>% randomize(invit) # remove agents with dates from invite, shuffle invit

############################ Accept invites ####################################
    for agent in invit
      if date == FALSE # Only look at agents without a date
     options <- invit %>% filter(to == agent & date == FALSE) # make a df with agents that sent me invites, and are still available
          
     if len(options) == 1 # if i have one option
          agent_option <- options$agent[1] # the name of the one agent that sent me an invite
          invit$date[agent] <- TRUE # set that i have a date
          invit$with[agent] <- agent_option # set that it is with the person on my options list
          invit$date[agent_option] <- TRUE # set that other agent has a date
          invit$with[agent_option] <- agent # set that it is with me
     
          else if len(options) > 1 # if i have more than one option
            choice <- dyads %>% # make a df from dyads
            filter(agent_1 == agent) %>% # only choose current agent
            filter(agent_2 %in% options) %>% # only choose agents that i have as options
            arrange(desc(sat)) # sort so agent with higest sat is on top #### OBS! What i secondary sort????? ####

          agent_option <- options$agent[1] # the name of the one agent that sent me an invite
          invit$date[agent] <- TRUE # set that i have a date
          invit$with[agent] <- agent_option # set that it is with the person on my options list
          invit$date[agent_option] <- TRUE # set that other agent has a date
          invit$with[agent_option] <- agent # set that it is with me
              
              arrange(desc(sat)) # sort so agent with higest sat is on top
        
          for agent in choice
        invit_agent <- choice$agent_2[1] # select top agent
      
        
          invit$date[invit$agent] <- TRUE # set that other agent has a date
          invit$with[invit$agent] <- agent # set that it is with me
          
    print(loop)
    
} # end of while loop
```

```{r}
# Hangout phase
for each dyad
  # generate matrix (a1b1, a2b1, a1b2, a2b2)
  for each agent
    a1b1 <- ac + pc + kj
    a2b1 <- ac + pc + kj
    a1b2 <- ac + pc + kj
    a2b2 <- ac + pc + kj
    
    choice <- higest()
  
```
